### 2019-10-28 Manuscript/manuscript.tex
updates to manuscript including revised paleolatitude figure

There is an overall lack of published continuous models in the literature for the Proterozoic that can be compared to the compilation of paleomagnetic poles presented herein. The approach in the community for many years has been to publish models as snapshots at given time intervals presented in figures without publishing continuous rotation parameters. With the further adoption of software tools such as GPlates, there has been significant progress in the publication of continuous paleogeographic models constrained by paleomagnetic poles through the Phanerozoic (540 Ma to present; e.g. \citealp{Torsvik2012a}).

>>>>

There is an overall lack of models in the literature for the Proterozoic have published continuous rotation parameters that can be compared to the compilation of paleomagnetic poles presented herein. The approach in the community for many years has been to publish models as snapshots at given time intervals presented in figures without publishing continuous rotation parameters although some studies have published the Euler rotations associated with specified times. With the further adoption of software tools such as GPlates, there has been significant progress in the publication of continuous paleogeographic models constrained by paleomagnetic poles through the Phanerozoic (540 Ma to present; e.g. \citealp{Torsvik2012a}).
